A Method for the Spectroscopic Inference of Stellar Parameters

### 2014-07-17 tex/paper.tex
sampling edition updated

\begin{enumerate}
  \item Choose starting parameters for $\allParameters^0$. Generally, these will be $\stellarParameters$ drawn from the literature, flat Chebyshev polynomials ($\Cheb$), and only Poisson noise ($\Cov$). 
  \item Start a new iteration of the Gibbs sampler with the parameters of the current proposal denoted with the superscript $j$ and the previous iteration denoted by $j-1$. 
  \item Sample the stellar parameters $p(\stellarParameters^j | \Cheb^{j-1}, \Cov^{j-1})$. 
  \item For each order of the echelle spectrum, $i$
    \begin{enumerate}
      \item Sample the Chebyshev polynomial parameters $p(\chebi{i}^j | \Chebi{i}^{j-1}, \stellarParameters^j, \Cov^{j-1} )$
      \item Check to see whether the algorithm should instantiate/delete new/old local kernels
      \item Sample the covariance parameters $p(\covi{i}^j | \Covi{i}^{j-1}, \stellarParameters^j, \Cheb^{j-1})$ 
    \end{enumerate}
    \item return to step 2 until Markov Chain is converged
\end{enumerate}

>>>>

\begin{enumerate}
  \item Choose starting parameters for $\allParameters^0$. Generally, these will be $\stellarParameters^0$ drawn from the literature, flat Chebyshev polynomials ($\Cheb^0$), and only Poisson noise ($\Cov^0$). 
  \item Start a new iteration of the Gibbs sampler with the parameters of the current proposal denoted with the superscript $j$ and the previous iteration denoted by $j-1$. If this is the first iteration of the Gibbs sampler, then $j - 1 = 0$.
  \item Sample the stellar parameters $p(\stellarParameters^j | \Cheb^{j-1}, \Cov^{j-1})$. 
  \item For each order of the echelle spectrum, $i$
    \begin{enumerate}
      \item Sample the Chebyshev polynomial parameters $p(\chebi{i}^j | \stellarParameters^j, \covi{i}^{j-1} )$
      \item Check to see whether the algorithm should instantiate/delete new/old local kernels
      \item Sample the covariance parameters $p(\covi{i}^j | \stellarParameters^j, \chebi{i}^{j})$ 
    \end{enumerate}
  after step 4 is completed, all Chebyshev and covariance parameters have been updated: $\Cheb^{j-1} \rightarrow \Cheb^j$ and $\Cov^{j-1} \rightarrow \Cov^j$
    \item return to step 2 until Markov Chain is converged
\end{enumerate}
